---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Raincouver

`Raincouver` is a package that allows you to easily obtain, process, analyse and generate awesome plots with weather data of vancouver. Here are things you can do:

- Get daily weather data from a certain year
- Do some analyses with data, like counting rainy days.
- Generate awesome plots yearly climate summary.
- Play with built-in dataset `raincouver10` contains weather data from 2010-01-01 to 2018-12-31.

## Example

Here are some basic examples:

```{r}
library(raincouver)
```


### Get data

With `get_data` you can easily access to daily weather data by year. Defaultly you will get the data of year 2018.

```{r}
df <- get_data()
knitr::kable(head(df))
```


### Do some analyses

There is some built-in functions in `raincouver` help to make data analyses easier.

`count_rainy` can count rainy days in weather data. Use `rf` argument to specify how much precipitation it needs to be a rainy day. Defaultly `rf` is set to `10mm`.

```{r}
count_rainy(df)
count_rainy(df, 1)
```



### Generate plots

With `plot_climate` function, you can easily summarise the climate infomation of a year.

```{r, fig.height=5, fig.width = 7}
plot_climate(df)
```


### Play with `raincouver10`

A built-in dataset for convenience.

```{r}
knitr::kable(summary(raincouver10))
```

